\documentclass[12pt, letterpaper]{article}
\usepackage{graphicx}

\begin{document}

\title{ETFs Proxies for the Secondary Bond Market and Corresponding Futures Contracts}
\author{Zayd Alzein}
\date{March 2025}

\maketitle %

\section{The Secondary Bond Market}

\textbf{The secondary bond market} is a financial market where investors buy and sell previously issued bonds. 
The secondary bond market is also known as the bond market. The bond market is an over-the-counter market, 
meaning that it is decentralized and trading is done electronically. \textbf{This introduces challenges} for our data collection process.
Because the bond market is decentralized, there is no central exchange where all trades are recorded.
Instead, trades are recorded by individual dealers and reported to the Financial Industry Regulatory Authority (FINRA).
Acquiring the pricing data for these securities is a challenge because the data is not readily available and/or is expensive to obtain.
Therefore, we need to find alternative sources of data to find the historical secondary bond market data.
For many of the most traded bonds, there are corresponding ETFs that track the performance of the bond.
For example, the iShares 7-10 Year Treasury Bond ETF (IEF) tracks the performance of the 7-10 year Treasury bond.
It turns out that these ETFs move in tandem with the underlying bond, and we can use the ETF data as a proxy for the bond data.

\hspace{1cm}

\section{Small List of ETFs, Corresponding Bonds, and Futures Contracts}

Here is a small list of ETFs that track the performance of various bonds, along with the related or corresponding futures contracts.
\begin{table}[h!]
    \centering %
    \begin{tabular}{||c c c||}
        \hline
        ETF Ticker & Underlying Bond & Futures Ticker \\
        \hline
        IEF & 7-10 Year Treasury Bond & TN1! \\
        TLT & 20+ Year Treasury Bond & TWE1! \\
        LQD & Investment Grade Corporate Bond & IBIG1! \\
        HYG & High Yield Corporate Bond & IBHY1! \\
    \end{tabular}
    \label{table:1}

\end{table} %


\end{document}